%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{multicol}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{}

\usepackage[left=0.50in,top=0.6in,right=0.50in,bottom=0.6in]{geometry} % Document margins

\name{Shayan Hosseini} % Your name
\address{X410D 2366 Main Mall, Vancouver, BC Canada V6T 1Z4} % Your address
\address{+1-604-841-1112 \\ \href{mailto:sshayanh@cs.ubc.ca}{\texttt{sshayanh@cs.ubc.ca}} \\ 
	\href{http://www.shayanh.ir}{\texttt{https://shayanh.com/}}} % Your phone number and email

\begin{document}
	
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
	{\bf \href{https://www.ubc.ca/}{University of British Columbia}}, Vancouver, BC, Canada
        \hfill 2021 - present
	\\M.Sc. in Computer Science
	
	{\bf \href{http://ut.ac.ir/en}{University of Tehran}}, Tehran, Iran \hfill 2015 - 2020 
	\\B.Sc. in Computer Engineering, GPA: 17.38/20 
    \\Thesis: \textit{Verfication of Microservices}
\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}
	{\bf Research Assistant at the \href{https://www.ubc.ca/}{University of British Columbia}},
        {Vancouver, BC, Canada \hfill 2021 - present}
	\\ \textit{Under supervision of Prof. I. Beschastnikh} \smallskip
	\vspace{-0.5em}
	\begin{itemize}[leftmargin=3mm]
		\setlength{\itemsep}{1pt}
		\setlength{\parskip}{0pt}
		\setlength{\parsep}{0pt}
		\renewcommand\labelitemi{$\cdot$}

		\item Working on the \href{https://github.com/UBC-NSS/pgo}{PGo} project,
            to compile verifiable models of the distributed system into implementations
            in Go.
		\item Built a verified model of Raft consensus protocol that can be compiled into Go.
			I came up with a solution to build verified fault-tolerant systems using PGo.
		\item Built several eventually consistent systems such as CRDTs, using PGo. 
	\end{itemize}

	{\bf Research Intern at \href{https://www.mpi-inf.mpg.de/}{Max Planck Institute for Informatics}}, {Saarbr{\"u}cken, Germanry \hfill Summer 2019}
	\\ \textit{Under supervision of Prof. C. Lenzen} \smallskip
	\vspace{-0.5em}
	\begin{itemize}[leftmargin=3mm]
		\setlength{\itemsep}{1pt}
		\setlength{\parskip}{0pt}
		\setlength{\parsep}{0pt}
		\renewcommand\labelitemi{$\cdot$}

		\item Working to make routing algorithms fault-tolerant by using an augmentation 
            process. I proved the lower bound for the minimum number of edges 
		    and vertices in the resulting augmented graph.
	\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Experience}
	{\bf Software Engineering Manager at \href{https://cafebazaar.ir/app?l=en}{Cafe Bazaar}}, Tehran, Iran \hfill 2020
	\smallskip
	\vspace{-0.5em}
	\begin{itemize}[leftmargin=3mm]
		\setlength{\itemsep}{1pt}
		\setlength{\parskip}{0pt}
		\setlength{\parsep}{0pt}
		\renewcommand\labelitemi{$\cdot$}

		\item Leading a team of 10 people working to integrate all public cloud services 
            into a unified product.
		\item Built a billing system to automatically charge users for
            their usage of the services.
		\item Built a monitoring and alerting system that allowed users
            to monitor their resources in the cloud.
	\end{itemize}
	
	{\bf Technical Lead and Product Manager at \href{https://cafebazaar.ir/app?l=en}{Cafe Bazaar}}, Tehran, Iran \hfill 2017 - 2019
	\smallskip
	\vspace{-0.5em}
	\begin{itemize}[leftmargin=3mm]
		\setlength{\itemsep}{1pt}
		\setlength{\parskip}{0pt}
		\setlength{\parsep}{0pt}
		\renewcommand\labelitemi{$\cdot$}

		\item Co-founded and led a team of 8 engineers to provide highly available and 
            scalable cloud service to other technical teams and companies (now rebranded 
            as \href{https://sotoon.ir/}{Sotoon}).
		\item Started and developed a distributed object storage service using Ceph. 
            It serves more than 50TB of data and responds to more than hundreds of 
            requests per second in production.
		\item Scaled our existing content delivery network 50\% by developing a new 
            architecture using cache servers.
		\item Designed and developed a new software architecture for the CDN nodes to be 
            dynamically configurable and multi-tenant.% With this architecture, we were able to serve more than one customer in our network.
		% \item Decreased latency of our CDN 10\% by using a new load balancing architecture based on IP Anycast.
	\end{itemize}
	
	{\bf Software Engineer at \href{https://cafebazaar.ir/app?l=en}{Cafe Bazaar}}, Tehran, Iran \hfill 2015 - 2017
	\smallskip
	\vspace{-0.5em}
	\begin{itemize}[leftmargin=3mm]
		\setlength{\itemsep}{1pt}
		\setlength{\parskip}{0pt}
		\setlength{\parsep}{0pt}
		\renewcommand\labelitemi{$\cdot$}

		\item Developing Cafe Bazaar back-end codebase, which had more than 100,000 lines of 
            Python code and 30 million users.
		\item System owner of Cafe Bazaar CDN and parts of the back-end. Managing these systems 
            on more than 15 servers.
		\item Responsible for code reviews and system maintenance.
	\end{itemize}
	
\end{rSection}

%----------------------------------------------------------------------------------------
%	AWARDS
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards and Honors}
	
	{\bf \href{http://icpc.baylor.edu/}{ICPC}}, International Collegiate Programming Contest
	\\The International Collegiate Programming Contest is the most prestigious programming 
        contest for college students.
	\smallskip
	\vspace{-0.5em}
	\begin{itemize}[leftmargin=3mm]
		\setlength{\itemsep}{1pt}
		\setlength{\parskip}{1pt}
		\setlength{\parsep}{0pt}
		\renewcommand\labelitemi{$\cdot$}

		\item {\bf 56\textsuperscript{th} team} in
		\href{https://icpc.global/community/results-2017}{the 41\textsuperscript{th} 
            ICPC World Finals},
		South Dakota, USA\hfill 2017
		\\ Top 0.3\% among more than 45,000 students from all over the world.
		
		\item {\bf 3\textsuperscript{rd} team} in
            \href{http://www.acmicpc-pacnw.org/scoreboard/2020/index1.html}
            {ICPC Pacific Northwest Regional Contest}
		\hfill 2021
		\\ Among more than 100 teams participating from the area of Pacific NW 
        (including Washington, Oregon, N. California, British Columbia).

		\item {\bf 3\textsuperscript{rd}, 2\textsuperscript{nd}, 2\textsuperscript{nd}, 
            9\textsuperscript{th} team} in Regional Contests of ICPC West Asia Region,
		    Tehran site, respectively in
            \href{http://icpc.sharif.edu/acmicpc18/scoreboard/}{2018},
            \href{http://icpc.sharif.edu/acmicpc17/scoreboard/}{2017},
            \href{http://icpc.sharif.edu/acmicpc16/scoreboard/}{2016} and
            \href{http://icpc.sharif.edu/acmicpc15/scoreboard/}{2015}.
		\\ Top 1\% among more than 300 teams that participate in this contest every year.
	\end{itemize}
	
	{\bf Silver Medal} in the 24\textsuperscript{th} \href{http://inoi.ir/}
        {Iranian National Olympiad in Informatics}\hfill 2014
	\smallskip
	\\Top 0.16\% in the algorithmic programming contest among 10,000 participants 
    in the country.

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\begin{rSection}{Notable Projects}
	{\bf \href{https://peydaa.ir/}{Peydaa}} \hfill 2021 - present
	\\ Peydaa is a non-profit platform to make transparency in the Iranian job market. 
    It is a website that people can anonymously share their salary and experience of working 
    in companies with others. I founded Peydaa myself, working as both product manager and 
    developer, and over time, four more people joined the team remotely. Until now, more 
    than 600 users have shared their salaries and experiences on Peydaa.

	{\bf \href{https://github.com/UBC-NSS/pgo}{PGo}} \hfill 2021 - present
	\\PGo compiles verifiable formal specifications into Go implementations. I contributed 
    to the PGo distributed runtime and built several distributed systems using PGo. 

	{\bf \href{https://github.com/DistributedClocks/tracing}{Tracing library}} \hfill 2021
	\\A light-weight library for manual distributed system tracing. Has been used for 
    precise automatic grading in 
    \href{https://www.cs.ubc.ca/~bestchai/teaching/cs416_2020w2/index.html}{CPSC 416 course}. 
    I was the main developer of the project.

    {\bf \href{https://github.com/shayanh/grpc-go-contracts}{gRPC Go Contracts}} \hfill 2020
    \\A design by contract library for the gRPC Go framework; To verify the communication of 
    microservices by writing contracts for their RPCs. I designed and implemented this project 
    as a part of my B.Sc. thesis.

	% {\bf \href{https://github.com/shayanh/limoo}{Limoo}} \hfill 2017
	% \\A desktop application that shows lyrics for the current playing song, server in \href{https://github.com/shayanh/limoo-server}{Go} and client in \href{https://github.com/shayanh/limoo}{Python}.

	% {\bf \href{https://github.com/KhassTeam/Persian-CAPTCHA}{CAPTCHA Farsi}} \hfill 2011-2012
	% \\Generating CAPTCHA in Persian by using image processing and calligraphy methods. Can be used in Persian websites. Awarded as Best Project in
	% \href{https://www.helli.ir/portal/content/%D8%AA%D9%82%D8%AF%DB%8C%D8%B1-%D8%A7%D8%B2-%D8%AF%D8%A7%D9%86%D8%B4-%D8%A2%D9%85%D9%88%D8%B2%D8%A7%D9%86-%D8%A8%D8%B1%D8%AA%D8%B1%D9%BE%DA%98%D9%88%D9%87%D8%B4%DA%AF%D8%B1}
	% 	{8th NODET Young Researchers Festival}.
\end{rSection}

%----------------------------------------------------------------------------------------
%	TEACHING
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching Experience}
	{\bf Teaching Assistant}
	\\\href{https://www.ubc.ca/}{University of British Columbia}
	\vspace{-0.5em}
	\begin{itemize}[leftmargin=3mm]
		\setlength{\itemsep}{1pt}
		\setlength{\parskip}{0pt}
		\setlength{\parsep}{0pt}
		\renewcommand\labelitemi{$\cdot$}

		\item CPSC 416: Distributed Systems, I. Beschastnikh \hfill Spring 2021
	\end{itemize}
	
	\href{http://ut.ac.ir/en}{University of Tehran}
	\vspace{-0.5em}
	\begin{itemize}[leftmargin=3mm]
		\setlength{\itemsep}{1pt}
		\setlength{\parskip}{0pt}
		\setlength{\parsep}{0pt}
		\renewcommand\labelitemi{$\cdot$}

		\item {\bf Head TA}, Design and Analysis of Algorithms, H. Mahini \hfill 2018 - 2019 
		\item Engineering Probability and Statistics, B. Bahrak \hfill Fall 2018, 2019
	\end{itemize}
	
	{\bf Informatics Olympiad and ICPC related}
	\\Teaching topics in computer science including Algorithms, Data Structures,
	and Graph Theory to undergraduate students preparing for ICPC as well as high school
	students preparing for Informatics Olympiad.

	\vspace{-0.5em}
	\begin{itemize}[leftmargin=3mm]
		\setlength{\itemsep}{1pt}
		\setlength{\parskip}{0pt}
		\setlength{\parsep}{0pt}
		\renewcommand\labelitemi{$\cdot$}

		\item \href{http://ut.ac.ir/en}{University of Tehran} \hfill 2017
		\item \href{http://inoi.ir/}{Iranian National Olympiad in Informatics Summer Camp} \hfill 2015
		\item \href{http://www.helli.ir/}{Allameh Helli High School} \hfill 2015
	\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills and Qualities}

	{\bf Programming Languages and Tools:}
	Expert in Go, Python, Bash-Scripting, Git. Working knowledge in C/C++, SQL, Java, 
    Lua, Javascript, Verilog, \LaTeX. \smallskip
	\\
	{\bf Software Engineering:}
	Familiar with different object-oriented design patterns, software development 
    methodologies such as Agile and DevOps and, functional programming.\smallskip
	\\
	{\bf Web Application Development:}
	Comfortable with Django, Flask, CSS3, HTML5 and ReactJS.\smallskip
	\\
	{\bf Site Reliability Engineering:}
	Managed scalability and maintainability challenges in several web applications having 
    thousands of requests per second.  Expert Linux user and experienced in system administration.
	Experience with Ceph storage platform, Kubernetes, Docker, NGINX, Networks.\smallskip
	\\
	{\bf Theoretical Background:}
	Expert in design of algorithms, data structures, and discrete mathematical fields such 
    as graph theory and combinatorics suggested by awards in ICPC and Olympiad in 
    Informatics.\smallskip
	\\
	{\bf Languages:}
	English (Full professional proficiency), Persian (Native).\smallskip

\end{rSection}
	
\end{document}
